---
title: "finalProject_week10_SenapatiKabindra"
output: html_document
---

# Get the housing data
```{r}
knitr::opts_chunk$set(echo = TRUE)
#library(readr)
#library(ggplot2)
#library(knitr)
#library(tidyverse)
```

#How to import and clean my data
```{r}
library(ggplot2)
housing_data <- read.csv("data/housing.csv")
head(housing_data)

```
#Data Cleansing
```{r}
str(housing_data)
library(ggplot2)
```
#What does the final data set look like?
--housing_data

#What information is not self-evident?
--longitude,latitude

#What are different ways you could look at this data?
--How the housing price is corrleatd to age and income

#How do you plan to slice and dice the data?
```{r}
library("dplyr")
glimpse(housing_data)
filter_data <- filter(housing_data, housing_median_age > 50)
head(filter_data)
```
#How could you summarize your data to answer key questions?
```{r}
summary(housing_data)
```
#What types of plots and tables will help you to illustrate the findings to your questions?
```{r}
br_mean = mean(housing_data$total_bedrooms, na.rm=TRUE)
br_median = median(housing_data$total_bedrooms, na.rm=TRUE)
ggplot(housing_data, aes(x = total_bedrooms)) +
  geom_histogram(bins = 40, color = "black", fill = "blue") +
  geom_vline(aes(xintercept = br_mean, color = "Mean"), lwd = 1.5) +
  geom_vline(aes(xintercept = br_median, color = "Median"), lwd = 1.5) +
  xlab("Total Bedrooms") +
  ylab("Frequency") +
  ggtitle("Histogram of Total Bedrooms (noncontinuous variable)") +
  scale_color_manual(name = "Summary", labels = c("Mean", "Median"), values = c("red", "green"))
```
#Do you plan on incorporating any machine learning techniques to answer your research questions? Explain.
--Yes. creating a linear model using the price , income nd age variables

#Questions for future steps.
How the model works for the different variables?
impact of Changing different variables in the model